# Results

The result chapter is of great importance in an empirical study and should comprise a good mix of text, tables and figures. Use your research questions and hypothesis for structuring this chapter to provide the reader some structure and to not lose the thread.

Figures and tables should be continuously numbered and referred to in the main text.  \LaTeX places figures and tables automatically were they fit best, which is sometimes on the next page. This is fine since they are cross-referenced anyway.
  
Tables have generally a caption at the top, while figures have a caption at the bottom. This has to be considered in some of the R functions (see below).


## Tables

### R Markdown table

Table \ref{tab:rmd_tab} is a R Markdown table including a caption and label for cross-referencing. The caption is set with **Table: ...** and can come before or after the table. You do not need so set a number as \LaTeX will take care of the numbering as well as the placing. Also note that the caption requires no quotation marks. 

The label is set **right after** the table caption with `\label{tab:name}`. **Note here** that this is \LaTeX notation, where brackets are **curly**, not round! Also when cross-referencing R Markdown tables use the \LaTeX notation `\ref{tab:name}` (i.e., no `@` and curly brackets).

Table: This is a table written in R Markdown.\label{tab:rmd_tab}

| A            | New              | Table          |
|:-------------|:----------------:|---------------:|
|left-aligned  |center-aligned    |right-aligned   |
|$123          |$456              |$789            |
|*italics*     |normal            |**boldface**    |


### Tables generated with R

Creating tables with R and packages like *knitr* and *kableExtra* is much easier (and protects against typing errors!) than manually entering values into a table by copying and pasting them into Excel or LaTeX. This shows once again how beautiful reproducible documents can be! 

#### Using the *knitr* and  *kableExtra* packages

&nbsp; <!-- This creates vertical space and is the same than \vspace{12pt} for latex -->

Table \@ref(tab:kable1) is an example of using `knitr::kable` to generate the table and *kableExtra* functions  to modify it. `knitr::kable()` has an explicit argument named `caption` where you can place your caption text.

```{r kable1}
# Import dataset from the data/ folder
mtcars <- read.csv("data/mtcars.csv")

# Plot only a subset of the data
df <- mtcars[1:5, 1:6]
kable(df, booktabs = T, 
  caption = "This is a table produced with knitr and modified with kableextra.") |>
kable_styling(position = "center", font_size = 9) |>
add_header_above(c(" " = 1, "Group 1" = 2, "Group 2" = 2,
  "Group 3" = 1, "Group 4" = 1)) |>
add_header_above(c(" ", "Group 5" = 4, "Group 6" = 2), bold = T) |>
kableExtra::footnote(general = "Your comments go here.")
```


#### The *flextable* package

&nbsp;

[flextable](https://ardata-fr.github.io/flextable-book/) creates tables that work across PDF and Word output, making it a versatile choice. Table \@ref(tab:flextable1) shows an example. Note that `flextable` uses the `set_caption()` function for cross-referenceable captions:

```{r flextable1}
df <- mtcars[1:5, 1:6]
flextable(df) |>
  set_caption(caption = "This is a table produced with flextable.") |>
  autofit() |>
  theme_booktabs() |>
  bold(part = "header") |>
  fontsize(size = 9, part = "all")
```

> **Tip:** Another excellent table package is [gt](https://gt.rstudio.com/), which provides a tidyverse-friendly grammar of tables. However, its PDF support is still maturing, so `kableExtra` (PDF) and `flextable` (PDF + Word) remain the most reliable choices for theses.


## Figures

Figures can directly be produced with R and displayed here. Since most students use *ggplot2*, the examples below use it. Similar to external images, figure captions and labels are placed inside the chunk options for cross-referencing (see Figure \@ref(fig:scatter-fig)).

```{r scatter-fig, fig.cap = "Relationship between horsepower and fuel economy.", out.width='100%'}
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(x = "Gross Horsepower", y = "Miles Per Gallon") +
  theme_minimal()
```

Purely for demonstration purposes, Figure \@ref(fig:boxplot-fig) shows a boxplot with just half the width and centered:

```{r boxplot-fig, fig.cap = "Fuel differences between transmission types (0 = automatic, 1 = manual).", out.width='50%', fig.height = 3, fig.align='center'}
ggplot(mtcars, aes(x = factor(am), y = mpg)) +
  geom_boxplot() +
  labs(x = "Transmission (0 = automatic, 1 = manual)", y = "Miles Per Gallon") +
  theme_minimal()
```


<!-- If you want the next chapter to start on a new page type -->
\newpage